---
title: "Alcohol vs Seat choice"
author: "Kimberly Aldana"
date: "Summer 2023"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
```{r eval=FALSE}
davisdata <- davisdata %>%
mutate(across(where(is.character), as.factor))
```


## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row
## you choose to sit in??

## Now with ggplot - first select the basic data
```{r}
ggplot(davisdata, aes(x = Seat, y = alcohol)) +
  geom_boxplot(notch = TRUE, outlier.colour = "red") +
  labs(title = "Notched Box Plot of Alcohol by Seat") +
  theme(plot.title = element_text(hjust = 0.5))



```





## Numerical Summarys 
```{r}
favstats(alcohol~Seat,data=davisdata)
```
 
 The people in the back are drinking a lot more than the people in the middle and the front. The data shows that min all equals 0, but with the median, the people in the back have 4 and the people in the middle have 1 while the front people have none. There is a big difference between the means, while the back people having the highest of almost a 10 rounded up while the people in the middle have 3 and front have a 2 rounded up.
 Most people are sitting in the middle with the number 83, and the rest are evened out between the back and front. You can find those numbers under the letter "n".

## Inferential Tests

```{r}
model1 <- aov(alcohol~Seat,data=davisdata)
summary.aov(model1)
```

```{r}
plot(TukeyHSD(model1))
```
There is a difference between the rows. The back rows





```{r}
# Load the necessary library
library(stats)

# Perform ANOVA test
anova_result <- aov(alcohol ~ Seat, data = davisdata)

# Check the ANOVA table
summary(anova_result)
```

```{r}
# Perform Tukey HSD test
tukey_result <- TukeyHSD(anova_result)

# Print the results
print(tukey_result)
```



## Conclusions


