---
title: "Alcohol vs Seat choice"
author: "Kimberly Aldana"
date: "Summer 2023"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
```{r eval=FALSE}
davisdata <- davisdata %>%
mutate(across(where(is.character), as.factor))
```


## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row
## you choose to sit in??

## Now with ggplot - first select the basic data
```{r}
ggplot(davisdata, aes(x = Seat, y = alcohol)) +
  geom_boxplot(notch = TRUE, outlier.colour = "red") +
  labs(title = "Notched Box Plot of Alcohol by Seat") +
  theme(plot.title = element_text(hjust = 0.5))



```

This box plot illustrates the distribution of alcohol across different seating locations represented by the "seat" variable in the data set. Each box represents the interquartile range (IQR) of alcohol consumption within each set, with a horizontal line inside denoting the median value. By visually taking an observation of the box plot, we can observe any apparent differences in alcohol consumption among the different seating locations provided.

## Numerical Summarys 
```{r}
favstats(alcohol~Seat,data=davisdata)
```
 
 The people in the back are drinking a lot more than the people in the middle and the front. The data shows that min all equals 0, but with the median, the people in the back have 4 and the people in the middle have 1 while the front people have none. There is a big difference between the means, while the back people having the highest of almost a 10 rounded up while the people in the middle have 3 and front have a 2 rounded up.
 Most people are sitting in the middle with the number 83, and the rest are evened out between the back and front. You can find those numbers under the letter "n".

## Inferential Tests

```{r}
model1 <- aov(alcohol~Seat,data=davisdata)
summary.aov(model1)
```

```{r}
plot(TukeyHSD(model1))
```

```{r}
# Load the necessary library
library(stats)

# Perform ANOVA test
anova_result <- aov(alcohol ~ Seat, data = davisdata)

# Check the ANOVA table
summary(anova_result)
```

```{r}
# Perform Tukey HSD test
tukey_result <- TukeyHSD(anova_result)

# Print the results
print(tukey_result)
```
Based on both the ANOVA and Turkey's HSD test results, there are significant differences in alcohol consumption between the Back seat and the Front seat, as well as between the Back seat and the Middle seat. However, there is no significant difference in alcohol consumption between the Front seat and the Middle seat.


## Conclusions

We walked through ANOVA which is more difficult  than the T-test. If there are more than two categories there is more work if the ANOVA has a lower p value. We had to run the turkey test and we asked Chat GPT for a code which was plugged in and it allowed us to see the differences in the three rows. These plots allowed us to see that there was a significant difference in the alcohol consumption between the seats. Additionally, the Turkey's HSD test results show significant differences in alcohol consumption between the Back seat and the Front seat, as well as between the Back seat and the Middle seat. However, there is no significant difference in alcohol consumption between the Front seat and the Middle seat.

